MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-06-04 MAESTROeX_I/appendix.tex
Added figures to appendix A

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\begin{tabular}{l r}
\multirow{4}{3.5in}[34.5mm]{ \includegraphics[width=3.0in]{./figs/wdconvect_256_splitU} } & \multicolumn{1}{c}{\includegraphics[width=2.35in]{./figs/magvel_full_XY}} \\
& \multicolumn{1}{c}{\begin{footnotesize} (a) $|\mathbf{U}|$, solved using $\mathbf{U}$ \end{footnotesize}} \\[1.em]
& \multicolumn{1}{c}{\includegraphics[width=2.35in]{./figs/magvel_split_XY}} \\ 
& \multicolumn{1}{c}{\begin{footnotesize} (b) $|\mathbf{U}|$, solved using $w_0 + \tilde{\mathbf{U}}$ \end{footnotesize}} \\
\end{tabular}
\caption{\label{fig:wdconvect_splitU} (Left) Peak temperature, $T_{\text{peak}}$ in a white dwarf at resolution of $256^3$ 
         during initial transition. (Right) Velocity magnitude solved using the full velocity $\mathbf{U}$ in projection step 
         results in large values outside the density cutoff region that is not seen with using the split velocities.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
